---
title: "Predictive Modeling For California Art Colleges"
author: Atul Lanka, Rushil Sheth, Timothy Park, Yuyu Zhang
date: December 6th 2016 
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Background  

## Introduction  
Goals: 

1. Determine succesful 4-year art schools in California

2. Develop a Shiny Web App to observe the Difference between Two art schools

## Original Data
Source: College Scorecard

Data from Most-Recent-Cohorts-All-Data-Elements.csv and consists of many variables

# Process

## Cleaned Data

Actually this data set contained way to many variables

1. Filtered for California 4-year art schools

2. Interested in Columns associated with:
	- Enrollment
	- Ethnicity
	- Age
	- Graduation Rate
	- Gender

## Method - Models  
The following models were considered to help our client: 
- Ordinary Least Squares Regression
- Ridge Regression 
- Lasso Regression
- Principal Components Regression
- Partial Least Squares Regression  


# Analysis  

## Summary 
```{r, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center"}
load('../data/OLS.Rdata')
load('../data/PCR.Rdata')
load('../data/Lasso.Rdata')
load('../data/Ridge.Rdata')
load('../data/PLSR.Rdata')
library(xtable)
Regression <- c('OLS','Ridge', 'Lasso', 'PCR', 'PLSR')
MSE <- c(ols_mse, ridge_MSE, test_mse, pcr_MSE, mse)
mse_chart <- data.frame(Regression, MSE)
mse_tbl <- xtable(mse_chart,
               caption = 'Test MSE Values for the Regression Techniques',
               digits = 7)

print(mse_tbl, caption.placement = 'top',
      comment = getOption('xtable.comment', FALSE),
      include.rownames = FALSE)


```

## App  
1. Choose 2 schools to compare
2. Choose what variable to compare:
	- Gender 
	- Ethnicity 
	- Graduation Rate
3. Decide the chart type 
4. Output: 2 charts(of the specified type) for each school using the choosen variable
