---
title: "Predictive Modeling For California Art Colleges"
author: Atul Lanka, Rushil Sheth, Timothy Park, Yuyu Zhang
date: December 6th 2016 
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Background  

## Introduction  
Goals:  
1. Determine succesful 4-year art schools in California
2. Develop a Shiny Web App to observe the Difference between Two art schools

## Original Data
Source: College Scorecard

Data from Most-Recent-Cohorts-All-Data-Elements.csv and consists of many variables

# Process

## Cleaned Data

Actually this data set contained way to many variables
1. Filtered for California 4-year art schools
2. Interested in Columns associated with:
	- Enrollment
	- Ethnicity
	- Age
	- Graduation Rate
	- Gender

## Method - Models  
The following models were considered to help our client: 
- Ordinary Least Squares Regression
- Ridge Regression 
- Lasso Regression
- Principal Components Regression
- Partial Least Squares Regression  


# Analysis  

## Summary 
```{r, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center"}
load('../data/OLS.Rdata')
load('../data/PCR.Rdata')
load('../data/Lasso.Rdata')
load('../data/Ridge.Rdata')
load('../data/PLSR.Rdata')
library(xtable)

coef_matrix <- matrix(data = c(as.numeric(OLS_summary$coefficients), 
                                  as.numeric(ridge_coef_full),
                                  as.numeric(lasso_coef),0, 
                                  as.numeric(pcr_coef_full), 0, 
                                  as.numeric(coeff)), 
                                  nrow = 12, ncol = 5)

colnames(coef_matrix) <- c('OLS', 'Ridge', 'Lasso', 'PC', 'PLS')
rownames(coef_matrix) <- c('Intercept', 'Income', 'Limit', 'Rating', 'Cards',
                           'Age', 'Education', 'GenderFemale', 'StudentYes',
                           'MarriedYes', 'EthnicityAsian',
                           'EthnicityCaucasian')
print(xtable(coef_matrix, caption = 'Regression Coefficients', digits = 4),
      type = 'latex', comment = FALSE)

```

## App  
1. Choose 2 schools to compare
2. Choose what variable to compare:
	- Gender 
	- Ethnicity 
	- Graduation Rate
3. Decide the chart type 
4. Output: 2 charts(of the specified type) for each school using the choosen variable
